---
title: "Reproducible Research Assignment 1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1.Code for reading in the dataset and/or processing the data

```{r data, echo=TRUE}
data <- read.csv('activity.csv')
```

## 2. Histogram of the total number of steps taken each day

```{r echo=TRUE}
steps <- tapply(data$steps, data$date, sum)
hist(steps, breaks=50)
```

## 3. Mean and median number of steps taken each day
```{r echo=TRUE}
mean(steps, na.rm=TRUE)
median(steps, na.rm=TRUE)
```

## 4. Time series plot of the average number of steps taken
```{r echo=TRUE}
aveSteps <- aggregate(x=list(steps=data$steps),
                      by=list(interval=data$interval),
                      mean,
                      na.rm=TRUE)
plot(aveSteps, type='l')
```

## 5. The 5-minute interval that, on average, contains the maximum number of steps
```{r echo=TRUE}
aveSteps[which.max(aveSteps$steps), ]
```

## 6. Code to describe and show a strategy for imputing missing data
```{r echo=TRUE}
missingData <- is.na(data$steps)
table(missingData)
```

## 7. Histogram of the total number of steps taken each day after missing values are imputed
```{r echo=TRUE}
dataRmMiss <- data[!missingData,]
stepsRmMiss <- tapply(dataRmMiss$steps, dataRmMiss$date, sum)
hist(stepsRmMiss, breaks=50)
```

## 8. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r echo=TRUE}
dataRmMiss$day <- 'weekdays'
dataRmMiss$day[weekdays(as.Date(dataRmMiss$date), abb=TRUE) %in% c('Sat', 'Sun')] <- 'weekends'
aveStepsWeek <- aggregate(x=list(steps=dataRmMiss$steps),
                          by=list(interval=dataRmMiss$interval, day=dataRmMiss$day),
                          mean,
                          na.rm=TRUE)

library(lattice)
xyplot(steps ~ interval | day, data=aveStepsWeek, type='l', 
       grid=TRUE, layout=c(1,2),
       ylab='steps', xlab='intervals')
```